Pipeline Performance Figure Generation

### 2023-08-02 TestingPipeline/Scripts/paper_figure_generation.Rmd
Updated figure S1.

colnames(MCC_sd_quant) <- c("testing_set_index", "1-2", "1-3", "1-4",
                            "1-5", "1-6", "1-7", "1-8")

MCC_sd_quant <- MCC_sd_quant %>% pivot_longer(cols=contains("-"))

ggplot(MCC_sd_quant, aes(x=testing_set_index, y=value, 
                                  color=name, fill=name)) +
  geom_point(alpha=0.5)

ggplot(MCC_sd_quant, aes(x=name, y=value)) +
  geom_boxplot(alpha=0.5, color=pal(4)[1]) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 0),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Testing Sets") +
  ylab("Standard Deviation") 
```

>>>>

colnames(MCC_sd_quant) <- c("testing_set_index", "2", "3", "4",
                            "5", "6", "7", "8")

MCC_sd_quant <- MCC_sd_quant %>% pivot_longer(cols=!contains("testing_set_index"))

ggplot(MCC_sd_quant, aes(x=name, y=value)) +
  geom_boxplot(alpha=0.5, color=pal(4)[1]) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 0),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  xlab("Number of Testing Sets Included") +
  ylab("Standard Deviation") 
```
```{r}
t.test(MCC_sd_quant$value[MCC_sd_quant$name==2],MCC_sd_quant$value[MCC_sd_quant$name==3])
t.test(MCC_sd_quant$value[MCC_sd_quant$name==3],MCC_sd_quant$value[MCC_sd_quant$name==4])
t.test(MCC_sd_quant$value[MCC_sd_quant$name==4],MCC_sd_quant$value[MCC_sd_quant$name==5])
t.test(MCC_sd_quant$value[MCC_sd_quant$name==5],MCC_sd_quant$value[MCC_sd_quant$name==6])
t.test(MCC_sd_quant$value[MCC_sd_quant$name==6],MCC_sd_quant$value[MCC_sd_quant$name==7])
t.test(MCC_sd_quant$value[MCC_sd_quant$name==7],MCC_sd_quant$value[MCC_sd_quant$name==8])
```
